When Do You Repeat Yourself?\\ Voices from the Trenches of Linux Kernel Maintainers on Code Duplication

### 2025-10-29 papers/techdebt2026/techdebt.tex
techdebt2026: techdebt: rephrase paragraph about undetailed groups
Group 5 and Group 11 were not detailed in the same sense as the other
groups, as they did not produce or influence the takeaways and the core
idea of the paper. However, the way it was put, made it feel like they
had literally no meaning in this regard, which was not true, so rephrase
this paragraph for a better contextualization.

Signed-off-by: David Tadokoro <davidbtadokoro@usp.br>

We did not explore the contributions of Group 5 and Group 11 in detail, as they did not result in any insights regarding these conflicting perspectives on software engineering practices. However, they were still meaningful as they produced impactful contributions that reduced a lot of duplicated code. Especially in Group 11, where a single student executed the whole workflow we did in the first phase, and managed to remove four hundred net lines of code.

>>>>

We did not explore the contributions of Group 5 and Group 11 in detail, as they did not result in (or influence) any insights regarding these fascinating perspectives from the Linux community that are dissonant with the apparently unquestionable DRY principle. However, they were still meaningful as they produced impactful contributions that reduced a lot of duplicated code. Especially in Group 11, where a single student executed the whole workflow we did in the first phase, and managed to remove four hundred net lines of code.
